Main Analyses of the Combined Dataset

### 2021-05-25 notebooks/main_analysis.Rmd
updates to ms, code

Body size and map length:

@@

@@

xd %>% filter(class == 'Mammalia') %>% arrange(desc(carbon_mass)) %>% 
  select(species, carbon_mass) %>% 
  as.data.frame()

>>>>

Body size and chromosome number:

@@

Range and map length:

d %>% 
  filter_at(vars(hcn, log10_size), ~ !is.na(.)) %>%
  ggplot(aes(log10_range, map_length, color=phylum)) + geom_point() + 
  geom_smooth(method='lm') + ylab('map length (Morgans)') + 
  xlab('log10(size)')

@@

xd %>% 
  filter(class == 'Mammalia') %>% 
  arrange(desc(carbon_mass)) %>% 
  select(species, carbon_mass, log10_popsize) %>% 
  as.data.frame()
